---
title: "nyc_park_regulation"
output: html_document
date: "2024-12-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up
```{r message=FALSE, warning=FALSE}
# Package names
packages <- c("tidyverse", "sf", "tmap", "tsibble", "tidycensus", "osmdata", "sfnetworks", "units", "tidygraph", "here")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
install.packages(packages[!installed_packages])
}

# Load packages
invisible(lapply(packages, library, character.only = TRUE))
```

# Import
```{r}
data_nyc_sf <- st_read("Parking_Regulation_Shapefile/Parking_Regulation_Shapefile.shp")
data_nyc_sf
```

```{r}
data_nyc_sf_not_mutcd <-data_nyc_sf %>%
   filter(!str_split_i(SG_MUTCD_C, pattern = "-", 1) %in% c("R7", "R8")) %>%
   select(SG_SEQNO_N, SG_MUTCD_C, X, Y, SIGNDESC1, SIGNDESC, SG_KEY_BOR) %>%
   relocate(SG_MUTCD_C, X, Y, SIGNDESC1, SIGNDESC, SG_SEQNO_N)
data_nyc_sf_not_mutcd
```

\
\

# Common signs
Sorting common parking signs pertaining to the MUTCD regulation 
```{r}
pattern <- "\\([^()]*\\)|<[^<>]*>"
```

```{r}
common_parksigns_before_sampling <- data_nyc_sf_not_mutcd %>%
  st_drop_geometry() %>%
  mutate(SG_MUTCD_C_1 = str_split_i(SG_MUTCD_C, pattern = "-", 1),
         SG_MUTCD_C_2 = str_split_i(SG_MUTCD_C, pattern = "-", 2)) %>%
  mutate(SG_MUTCD_C_2_abb = str_remove_all(SG_MUTCD_C_2, "[A-Za-z]")) %>%     # this part has been changed
  mutate(SG_MUTCD_C_abb = str_c(SG_MUTCD_C_1, "-", SG_MUTCD_C_2_abb)) %>%
  select(-c("SG_MUTCD_C_1", "SG_MUTCD_C_2", "SG_MUTCD_C_2_abb")) %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C) %>%
  arrange(SG_MUTCD_C_abb) %>%
  group_by(SG_MUTCD_C_abb) %>%
  arrange(SG_MUTCD_C) %>%
  mutate(SIGNDESC1_abb = first(SIGNDESC1)) %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, SIGNDESC1_abb, SIGNDESC1) %>%
  mutate(SIGNDESC1_abb = gsub(pattern, "", SIGNDESC1_abb)) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C_abb, SG_MUTCD_C) %>%
  summarise(SIGNDESC1_abb = first(SIGNDESC1_abb),
            SIGNDESC1 = first(SIGNDESC1), 
            count = n()) %>%
  ungroup() %>%
  select(-SIGNDESC1) %>%
  select(-count)
common_parksigns_before_sampling
```

```{r}
common_parksigns_before_sampling %>%
  write_csv("assets/common_parksigns/common_parksigns_before_sampling_not_mutcd.csv")
```

```{r}
common_parksigns_before_sampling %>%
  group_by(SG_MUTCD_C_abb) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

\
\

# Sampling
## exclude Manhattan
```{r}
data_nyc_sf_not_mutcd <- data_nyc_sf_not_mutcd %>%
  filter(SG_KEY_BOR != "M")
data_nyc_sf_not_mutcd
```

## count instances per category
```{r}
data_nyc_sf_not_mutcd <- data_nyc_sf_not_mutcd %>%
  left_join(common_parksigns_before_sampling, by = "SG_MUTCD_C") %>%
  group_by(SG_MUTCD_C_abb) %>%
  mutate(count_abb = n()) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb) %>%
  arrange(SG_MUTCD_C_abb, SG_MUTCD_C)
data_nyc_sf_not_mutcd
```

```{r}
data_nyc_sf_not_mutcd %>%
  st_write("assets/parksign_coords/data_nyc_sf_not_mutcd.geojson")
```

```{r}
data_nyc_sf_not_mutcd <- st_read("assets/parksign_coords/data_nyc_sf_not_mutcd.geojson")
```

## histogram
```{r}
data_nyc_sf_not_mutcd_counts <- data_nyc_sf_not_mutcd %>%
  distinct(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count)
data_nyc_sf_not_mutcd_counts
```

```{r}
data_nyc_sf_not_mutcd_counts %>%
  distinct(SG_MUTCD_C_abb, count_abb) %>%
  arrange(desc(count_abb))
```

```{r fig.width = 10, fig.height = 4}
g1 <- data_nyc_sf_not_mutcd_counts %>%
  ggplot(aes(x = count_abb)) +
  geom_histogram()
g2 <- data_nyc_sf_not_mutcd_counts %>%
  filter(count_abb < 100) %>%
  ggplot(aes(x = count_abb)) +
  geom_histogram()
ggpubr::ggarrange(g1, g2, ncol = 2)
```

```{r fig.width = 10, fig.height = 4}
g1 <- data_nyc_sf_not_mutcd_counts %>%
  ggplot(aes(x = count)) +
  geom_histogram()
g2 <- data_nyc_sf_not_mutcd_counts %>%
  filter(count < 100) %>%
  ggplot(aes(x = count)) +
  geom_histogram()
ggpubr::ggarrange(g1, g2, ncol = 2)
```

## sorting out rare signs
```{r}
data_nyc_sf_not_mutcd_counts %>%
  arrange(count) %>%
  filter(count < 50)
```

```{r}
data_nyc_sf_not_mutcd_counts %>%
  arrange(count) %>%
  filter(count > 9) %>%
  group_by(SG_MUTCD_C_abb) %>%
  summarise(count_abb = first(count_abb)) %>%
  arrange(count_abb)
```

```{r}
data_nyc_sf_not_mutcd_sortedout <- data_nyc_sf_not_mutcd %>%
  filter(count > 49) %>%
  select(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb, X, Y, SG_KEY_BOR)
data_nyc_sf_not_mutcd_sortedout
```

```{r}
data_nyc_sf_not_mutcd_sortedout <- data_nyc_sf_not_mutcd_sortedout %>%
  group_by(SG_MUTCD_C_abb) %>%
  mutate(count_abb = n()) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb) %>%
  arrange(SG_MUTCD_C_abb, SG_MUTCD_C)
data_nyc_sf_not_mutcd_sortedout
```

```{r}
data_nyc_sf_not_mutcd_sortedout_counts <- data_nyc_sf_not_mutcd_sortedout %>%
  distinct(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count)
data_nyc_sf_not_mutcd_sortedout_counts
```

```{r fig.width = 10, fig.height = 4}
g1 <- data_nyc_sf_not_mutcd_sortedout_counts %>%
  ggplot(aes(x = count)) +
  geom_histogram()
g2 <- data_nyc_sf_not_mutcd_sortedout_counts %>%
  filter(count < 100) %>%
  ggplot(aes(x = count)) +
  geom_histogram()
ggpubr::ggarrange(g1, g2, ncol = 2)
```

```{r}
data_nyc_sf_not_mutcd_sortedout <- data_nyc_sf_not_mutcd_sortedout %>%
  mutate(sign_unique_id = 1:nrow(.)) %>%
  mutate(sign_unique_id = as.character(sign_unique_id)) %>%
  relocate(sign_unique_id)
data_nyc_sf_not_mutcd_sortedout
```

```{r}
data_nyc_sf_not_mutcd_sortedout %>%
  st_write("assets/parksign_coords/data_nyc_sf_not_mutcd_sortedout.geojson")
```

```{r}
tmap_mode("view")
tm_shape(data_nyc_sf_not_mutcd_sortedout) +
  tm_dots()
```

## two sampling frames (all or random sample of size 200)
```{r}
data_nyc_sf_not_mutcd_sortedout_counts_below500 <- data_nyc_sf_not_mutcd_sortedout_counts %>%
  ungroup() %>%
  arrange(count_abb) %>%
  filter(count_abb < 501) %>%
  pull(SG_MUTCD_C_abb)
data_nyc_sf_not_mutcd_sortedout_counts_below500
```

```{r}
data_nyc_sf_not_mutcd_sortedout_counts_moreequal100 <- data_nyc_sf_not_mutcd_sortedout_counts %>%
  ungroup() %>%
  arrange(count_abb) %>%
  filter(count_abb > 500) %>%
  pull(SG_MUTCD_C_abb)
data_nyc_sf_not_mutcd_sortedout_counts_moreequal100
```

```{r}
#data_sample_1 <- data_nyc_sf_not_mutcd_sortedout %>%
#  filter(SG_MUTCD_C %in% data_nyc_sf_not_mutcd_sortedout_counts_below100) %>%
#  group_by(SG_MUTCD_C) %>%
#  arrange(count)
#data_sample_1
```

```{r}
set.seed(123)
data_sample_2 <- data_nyc_sf_not_mutcd_sortedout %>%
  filter(SG_MUTCD_C_abb %in% data_nyc_sf_not_mutcd_sortedout_counts_moreequal100) %>%
  group_by(SG_MUTCD_C_abb) %>%
  slice_sample(n = 100) 
data_sample_2 
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled <- data_sample_2
data_nyc_sf_not_mutcd_sortedout_sampled
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
  group_by(SG_MUTCD_C_abb) %>%
  mutate(count_abb = n()) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb) %>%
  arrange(SG_MUTCD_C_abb, SG_MUTCD_C)
data_nyc_sf_not_mutcd_sortedout_sampled
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled_counts <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
  distinct(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count)
data_nyc_sf_not_mutcd_sortedout_sampled_counts
```

```{r fig.width = 10, fig.height = 4}
g1 <- data_nyc_sf_not_mutcd_sortedout_sampled_counts %>%
  ggplot(aes(x = count)) +
  geom_histogram()
g2 <- data_nyc_sf_not_mutcd_sortedout_sampled_counts %>%
  filter(count < 100) %>%
  ggplot(aes(x = count)) +
  geom_histogram()
ggpubr::ggarrange(g1, g2, ncol = 2)
```


```{r}
data_nyc_sf_not_mutcd_sortedout_sampled %>%
  st_write("assets/parksign_coords/data_nyc_sf_not_mutcd_sortedout_sampled.geojson")
```

## result
```{r}
tmap_mode("view")
tm_shape(data_nyc_sf_not_mutcd_sortedout_sampled) +
  tm_dots()
```

# HERE !!!
# OSM road network
```{r}
#nyc_sf <- tigris::places('NY', progress_bar = F) %>%
#  filter(NAME == "New York") %>%
#  st_transform(4326)
#nyc_sf
```

```{r}
#nyc_sf %>%
#  st_write("assets/nyc_sf.geojson")
```

```{r eval=FALSE}
#nyc_sf_bbox <- nyc_sf %>%
#  st_bbox()
#nyc_sf_bbox
```

```{r eval=FALSE}
#nyc_osm <- opq(bbox = nyc_sf_bbox) %>%
#  add_osm_feature(key = 'highway', 
#                  value = c("motorway", "trunk", "primary", 
#                            "secondary", "tertiary", "unclassified",
#                            "residential")) %>%
#  osmdata_sf() %>% 
#  osm_poly2line()
#nyc_osm
```

```{r}
#nyc_osm %>%
#  saveRDS("assets/osm/nyc_osm.rds")
```

```{r}
#nyc_osm <- readRDS("assets/osm/nyc_osm.rds")
#nyc_osm
```

```{r eval=FALSE}
#nyc_osm_lines <- nyc_osm$osm_lines %>% 
#  select(osm_id, highway) %>% 
#  sfnetworks::as_sfnetwork(directed = FALSE) %>% 
#  activate("edges") %>%
#  filter(!edge_is_multiple()) %>% # remove duplicated edges
#  filter(!edge_is_loop()) %>% # remove loops
#  convert(., sfnetworks::to_spatial_subdivision) %>% # subdivide edges
#  convert(., sfnetworks::to_spatial_smooth) %>% # delete pseudo nodes
#  mutate(length = edge_length()) %>%
#  select(osm_id, highway, length) 
#nyc_osm_lines
```

```{r}
#nyc_osm_lines %>%
#  saveRDS("assets/osm/nyc_osm_lines.rds")
```

```{r}
#nyc_osm_lines <- readRDS("assets/osm/nyc_osm_lines.rds")
#nyc_osm_lines
```

```{r}
#nyc_osm_lines_only <- nyc_osm_lines %>%
#  activate("edges") %>%
#  as_tibble() %>%
#  st_as_sf()
#nyc_osm_lines_only
```

```{r}
#nyc_osm_lines_only %>%
#  st_write("assets/osm/nyc_osm_lines_only.geojson")
```

```{r}
#nyc_osm_lines_only <- st_read("assets/osm/nyc_osm_lines_only.geojson")
#nyc_osm_lines_only
```

```{r}
#nyc_osm_lines_only_filtered <- nyc_osm_lines_only %>% 
#  st_as_sf("edges") %>% 
#  mutate(length = as.vector(length)) %>% 
#  filter(length > 20) %>% 
  #mutate(edge_id = seq(1,nrow(.))) %>%
#  select(-c("from", "to")) 
#nyc_osm_lines_only_filtered
```

```{r}
#data_nyc_sf_not_mutcd_sortedout_sampled_buffer <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
#  st_buffer(dist = 12)
#data_nyc_sf_not_mutcd_sortedout_sampled_buffer
```

```{r}
#data_nyc_sf_not_mutcd_sortedout_sampled_buffer %>%
#  st_write("assets/parksign_coords/data_nyc_sf_not_mutcd_sortedout_sampled_buffer.geojson")
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled_buffer <- st_read("assets/parksign_coords/data_nyc_sf_not_mutcd_sortedout_sampled_buffer.geojson")
```

```{r}
#nyc_osm_lines_only_filtered <- nyc_osm_lines_only_filtered[data_nyc_sf_not_mutcd_sortedout_sampled_buffer, ] 
#nyc_osm_lines_only_filtered
```

```{r}
#nyc_osm_lines_only_filtered %>%
#  st_write("assets/osm/nyc_osm_lines_only_filtered.geojson")
```

```{r}
nyc_osm_lines_only_filtered <- st_read("assets/osm/nyc_osm_lines_only_filtered.geojson")
```

```{r}
tmap_mode('view')

tm_shape(nyc_sf) + 
  tm_borders() +
tm_shape(nyc_osm_lines_only_filtered) +
  tm_lines() +
tm_shape(data_nyc_sf_not_mutcd_sortedout_sampled_buffer) +
  tm_polygons(col = "orange", alpha = 0.2) +
tm_shape(data_nyc_sf_not_mutcd_sortedout_sampled) +
  tm_dots(size = 0.05, col = "red")
```

# GSV images
## sample case
```{r}
data_nyc_sf_not_mutcd_sortedout_sampled
```

```{r}
sample_sign <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
  filter(sign_unique_id == "1791") %>%
  select(sign_unique_id, SG_MUTCD_C_abb, SG_MUTCD_C, SIGNDESC1_abb)
sample_sign
```

```{r}
sample_buffer <- sample_sign %>%
  st_buffer(dist = 12) %>%
  st_boundary()
sample_buffer
```

```{r}
sample_osm <- nyc_osm_lines_only_filtered[sample_buffer, ]
sample_osm
```

```{r}
sample_intersections <- st_intersection(sample_buffer, sample_osm) %>%
  st_cast("POINT") %>%
  relocate(osm_id, highway, sign_unique_id, SG_MUTCD_C_abb, SG_MUTCD_C, SIGNDESC1_abb)
sample_intersections
```

```{r}
sample_intersections_1 <- sample_intersections[1,]
sample_intersections_2 <- sample_intersections[2,]
print(sample_intersections_1)
print(sample_intersections_2)
```

```{r}
tmap_mode('view')

tm_shape(sample_osm) +
  tm_lines() +
tm_shape(sample_buffer) +
  tm_lines(col = "black", alpha = 1) +
tm_shape(sample_sign) +
  tm_dots(size = 0.05, col = "red") +
tm_shape(sample_intersections_1) +
  tm_dots(size = 0.05, col = "blue") +
tm_shape(sample_intersections_2) +
  tm_dots(size = 0.05, col = "green")
```


```{r}
# Extract coordinates
coords1 <- st_coordinates(sample_intersections_1)
coords2 <- st_coordinates(sample_intersections_2)

# Ratio for internal division (m:n)
m <- 1
n <- 2

# Calculate the internal division point. lon lat 
x_div <- (m * coords2[1, "X"] + n * coords1[1, "X"]) / (m + n)
y_div <- (m * coords2[1, "Y"] + n * coords1[1, "Y"]) / (m + n)

# Create the division point as an sf object
division_point <- st_point(c(x_div, y_div))
division_point_sf <- st_sfc(division_point, crs = 4326)

sample_division_1 <- sample_intersections_1 
st_geometry(sample_division_1) <- st_sfc(division_point_sf)

# Ratio for internal division (m:n)
m <- 2
n <- 1

# Calculate the internal division point. lon lat 
x_div <- (m * coords2[1, "X"] + n * coords1[1, "X"]) / (m + n)
y_div <- (m * coords2[1, "Y"] + n * coords1[1, "Y"]) / (m + n)

# Create the division point as an sf object
division_point <- st_point(c(x_div, y_div))
division_point_sf <- st_sfc(division_point, crs = 4326)

sample_division_2 <- sample_intersections_2
st_geometry(sample_division_2) <- st_sfc(division_point_sf)
```

```{r}
tmap_mode('view')

tm_shape(sample_osm) +
  tm_lines() +
tm_shape(sample_buffer) +
  tm_lines(col = "black", alpha = 1) +
tm_shape(sample_sign) +
  tm_dots(size = 0.05, col = "red") +
tm_shape(sample_intersections_1) +
  tm_dots(size = 0.05, col = "blue") +
tm_shape(sample_intersections_2) +
  tm_dots(size = 0.05, col = "green") +
tm_shape(sample_division_1) +
  tm_dots(size = 0.05, col = "blue") +
tm_shape(sample_division_2) +
  tm_dots(size = 0.05, col = "green") 
```

```{r}
getCoordinates <- function(x){
  x <- x %>%
    mutate(lon = st_coordinates(geometry)[, "X"],
           lat = st_coordinates(geometry)[, "Y"]) 
  return(x)
}
```

```{r}
sample_sign <- getCoordinates(sample_sign)
sample_sign

sample_division_1 <- getCoordinates(sample_division_1)
sample_division_1

sample_division_2 <- getCoordinates(sample_division_2)
sample_division_2
```

```{r}
getAzimuth <- function(sign, viewpoint){
  azimuth <- atan2(sign %>% pull(lon) %>% as.numeric() - viewpoint %>% pull(lon) %>% as.numeric() ,
                   sign %>% pull(lat) %>% as.numeric() - viewpoint %>% pull(lat) %>% as.numeric() )*180/pi
  if (azimuth < 0){
  azimuth <- azimuth + 360
  #print(azimuth)
  }
  
  viewpoint$azi <- azimuth
  #print(viewpoint)
  return(viewpoint)
}
```

```{r}
sample_division_1 <- getAzimuth(sample_sign, sample_division_1)
sample_division_1

sample_division_2 <- getAzimuth(sample_sign, sample_division_2)
sample_division_2
```

```{r}
key <- Sys.getenv("google_api_jaegleejamsil")
```

```{r}
dir_here <- "/Users/jaeglee/ongoings/parking_sign/nyc/data/"
```

```{r}
getImage <- function(iterrow){
  location <- paste0(iterrow$lat %>% round(9), ",", iterrow$lon %>% round(9))
  heading <- iterrow$azi %>% round(3)
  highway <- iterrow$highway
  signid <- iterrow$sign_unique_id
  fov <- 45
  
  endpoint <- "https://maps.googleapis.com/maps/api/streetview"
  
  furl <- glue::glue("{endpoint}?size=640x640&location={location}&heading={heading}&fov={fov}&pitch=0&key={key}")
  fname <- glue::glue("GSV-signid_{signid}-location_{location}-heading_{heading}-fov_{fov}.jpg") # Don't change this code for fname
  fpath <- paste0(dir_here, "img_1/", fname)

  if (!file.exists(fpath)){
    download.file(furl, fpath, mode = 'wb') 
  }
}
```

```{r}
sample_division_1 %>%
  getImage()
```

```{r}
sample_division_2 %>%
  getImage()
```

```{r}
#sample_sign %>%
#  mutate(azi = (as.numeric(sample_division_1$azi) + as.numeric(sample_division_2$azi))/2)%>%
#  getImage()
```
  
## functionalize
```{r}
getIntersections <- function(buffer){
  temp_osm <- nyc_osm_lines_only_filtered[buffer, ]
  
  if (nrow(temp_osm) > 0){
    temp_osm <- temp_osm %>% slice(1)
    
    temp_intersections <- st_intersection(buffer, temp_osm) %>%
      st_cast("POINT") %>%
      relocate(osm_id, highway, sign_unique_id, SG_MUTCD_C_abb, SG_MUTCD_C, SIGNDESC1_abb)
    
    #print(temp_intersections)
    return(temp_intersections)
  } else{
    temp_intersections <- temp_osm
  }
}

getDivisions <- function(temp_intersections) {
  if (nrow(temp_intersections) == 2){
    temp_intersections_1 <- temp_intersections[1,]
    temp_intersections_2 <- temp_intersections[2,]
  
    coords1 <- st_coordinates(temp_intersections_1)
    coords2 <- st_coordinates(temp_intersections_2)
      
    m <- 1
    n <- 2
    x_div <- (m * coords2[1, "X"] + n * coords1[1, "X"]) / (m + n)
    y_div <- (m * coords2[1, "Y"] + n * coords1[1, "Y"]) / (m + n)
    division_point <- st_point(c(x_div, y_div))
    division_point_sf <- st_sfc(division_point, crs = 4326)
    temp_division_1 <- temp_intersections_1 
    st_geometry(temp_division_1) <- st_sfc(division_point_sf)
  
    m <- 2
    n <- 1
    x_div <- (m * coords2[1, "X"] + n * coords1[1, "X"]) / (m + n)
    y_div <- (m * coords2[1, "Y"] + n * coords1[1, "Y"]) / (m + n)
    division_point <- st_point(c(x_div, y_div))
    division_point_sf <- st_sfc(division_point, crs = 4326)
    temp_division_2 <- temp_intersections_2
    st_geometry(temp_division_2) <- st_sfc(division_point_sf)
    
    temp_divisions_tb <- temp_division_1 %>%
      bind_rows(temp_division_2)
  
    return(temp_divisions_tb)
    rm(temp_intersections_1, temp_intersections_2, temp_division_1, temp_division_2)  
  }
}

getCoordinates <- function(x){
  x <- x %>%
    mutate(lon = st_coordinates(geometry)[, "X"],
           lat = st_coordinates(geometry)[, "Y"]) 
  return(x)
}

getAzimuth <- function(sign, viewpoint){
  azimuth <- atan2(sign %>% pull(lon) %>% as.numeric() - viewpoint %>% pull(lon) %>% as.numeric() ,
                   sign %>% pull(lat) %>% as.numeric() - viewpoint %>% pull(lat) %>% as.numeric() )*180/pi
  if (azimuth < 0){
  azimuth <- azimuth + 360
  #print(azimuth)
  }
  
  viewpoint$azi <- azimuth
  #print(viewpoint)
  return(viewpoint)
}

getImage <- function(iterrow){
  location <- paste0(iterrow$lat %>% round(9), ",", iterrow$lon %>% round(9))
  heading <- iterrow$azi %>% round(3)
  highway <- iterrow$highway
  signid <- iterrow$sign_unique_id
  fov <- 40
  
  endpoint <- "https://maps.googleapis.com/maps/api/streetview"
  
  furl <- glue::glue("{endpoint}?size=640x640&location={location}&heading={heading}&fov={fov}&pitch=0&key={key}")
  fname <- glue::glue("GSV-signid_{signid}-location_{location}-heading_{heading}-fov_{fov}.jpg") # Don't change this code for fname
  fpath <- paste0(dir_here, "img_1/", fname)

  if (!file.exists(fpath)){
    download.file(furl, fpath, mode = 'wb') 
  }
}
```

## range
```{r}
nrow(data_nyc_sf_not_mutcd_sortedout_sampled)
```

```{r}
batch1 <- 1:999
batch2 <- 1000:1999
batch3 <- 2000:2999
batch4 <- 3000:3789
```

## for loop
```{r}
whichbatch <- batch2
```

```{r}
# nrow(data_nyc_sf_not_mutcd_sortedout_sampled_slimed)
for (i in 3500:3789) {
  print(glue::glue("starting {i}th image: unique_id {as.character(data_nyc_sf_not_mutcd_sortedout_sampled$sign_unique_id[i])}"))

  temp_sign <- data_nyc_sf_not_mutcd_sortedout_sampled %>% 
    slice(i)
    
  temp_sign_buffer <- temp_sign %>% 
    st_buffer(dist = 12) %>%
    st_boundary()
  
  temp_intersections <- getIntersections(temp_sign_buffer)
  
  if (nrow(temp_intersections) == 2){
    result_divisions_tb <- getDivisions(temp_intersections)
    division_1 <- result_divisions_tb %>% slice(1)
    division_2 <- result_divisions_tb %>% slice(2)
  } else{
    next
  }

  temp_sign <- getCoordinates(temp_sign)
  division_1 <- getCoordinates(division_1)
  division_2 <- getCoordinates(division_2) 
  
  division_1 <- getAzimuth(temp_sign, division_1)
  division_2 <- getAzimuth(temp_sign, division_2)
  
  division_1 %>%
    getImage()
  division_2 %>%
    getImage()
}
```

```{r}
# for verification
#tmap_mode('view')

#tm_shape(temp_sign) +
#  tm_dots(size = 0.05, col = "black") +
#tm_shape(temp_sign_buffer) +
#  tm_lines(col = "black", alpha = 1) +
#tm_shape(result_divisions_tb) +
#  tm_dots(size = 0.05, col = "red") 
```


# Distribution of classes within the sample
```{r}
data_nyc_sf_not_mutcd_sortedout_sampled
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled %>%
  group_by(SG_MUTCD_C_abb) %>%
  mutate(count_abb = n()) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb) %>%
  arrange(SG_MUTCD_C_abb, SG_MUTCD_C) %>%
  distinct(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count)
```

```{r}
data_nyc_sf_not_mutcd_sortedout_sampled %>%
  group_by(SG_MUTCD_C_abb) %>%
  mutate(count_abb = n()) %>%
  ungroup() %>%
  group_by(SG_MUTCD_C) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  relocate(SG_MUTCD_C_abb, SG_MUTCD_C, count_abb, count, SIGNDESC1_abb) %>%
  arrange(SG_MUTCD_C_abb, SG_MUTCD_C) %>%
  distinct(SG_MUTCD_C_abb, count_abb)
```


# Change file names
```{r}
mapping_signid_MUTCD <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
  st_drop_geometry() %>%
  select(sign_unique_id, SG_MUTCD_C_abb) 
mapping_signid_MUTCD
```

```{r}
filenames <- list.files("img_1/")
print(filenames[1:5])
```

```{r}
for (name in filenames[1:5]){
  name_split <- strsplit(name, "-")[[1]][2]
  signid <- strsplit(name_split, "_")[[1]][2]

  mutcd <- mapping_signid_MUTCD %>%
  filter(sign_unique_id == signid) %>%
  pull(SG_MUTCD_C_abb) %>%
  as.character()
  
  print(glue::glue("signid:{signid} belongs to {mutcd}"))
  
  newname <- str_c(strsplit(name, "-")[[1]][2],
                   "-",
                   glue::glue("mutcd_{mutcd}"), 
                   "-",
                   strsplit(name, "-")[[1]][3],
                   "-",
                   strsplit(name, "-")[[1]][4],
                   "-",
                   strsplit(name, "-")[[1]][5],
                   ".jpg")
  print(newname)
}
```

```{r}
filenames_new <- vector()
```

```{r}
for (name in filenames){
  name_split <- strsplit(name, "-")[[1]][2]
  signid <- strsplit(name_split, "_")[[1]][2]

  mutcd <- mapping_signid_MUTCD %>%
  filter(sign_unique_id == signid) %>%
  pull(SG_MUTCD_C_abb) %>%
  as.character()
  
  #print(glue::glue("signid:{signid} belongs to {mutcd}"))
  
  newname <- str_c(strsplit(name, "-")[[1]][2],
                   "-",
                   glue::glue("mutcd_{mutcd}"), 
                   "-",
                   strsplit(name, "-")[[1]][3],
                   "-",
                   strsplit(name, "-")[[1]][4],
                   "-",
                   strsplit(name, "-")[[1]][5],
                   ".jpg")
  #print(newname)
  
  filenames_new <- filenames_new %>%
    c(newname)
}
```

```{r}
length(filenames)
length(filenames_new)
```

```{r}
setwd("/Users/jaeglee/ongoings/parking_sign/nyc/data/img_1")
file.rename(filenames, filenames_new)
```

```{r}
length(filenames)
```

# List of parking sign classes
```{r}
common_parksigns_after_sampling <- data_nyc_sf_not_mutcd_sortedout_sampled %>%
  st_drop_geometry() %>%
  select(SG_MUTCD_C_abb, SIGNDESC1_abb) %>%
  group_by(SG_MUTCD_C_abb) %>%
  summarise(SIGNDESC1_abb = first(SIGNDESC1_abb),
            count_abb = n())
common_parksigns_after_sampling
```

```{r}
common_parksigns_after_sampling %>%
  write_csv("assets/common_parksigns/common_parksigns_after_sampling_not_mutcd.csv")
```









